---
title: "Two Parameters"
author: "Elaine Zhang"
format: html
---
we have data about people, their heights, and other covariates. We want to find the proportion of men with different heights. However, we can't assume validity since the measurements might have varied (like if they were wearing shoes or not).However, stability may not hold since an influx of immigrants may change the height average.We modeled the dependent variable, height, using an intercept-only regression. The average height of adult men in 2024 is 176 cm, with standard deviation of 7.48 cm.

```{r}
#| echo: FALSE
#| message: FALSE

library(tidyverse)
library(primer.data)
library(tidybayes)
library(brms)
library(gtsummary)
```

```{r}
nhanes |>
  filter(sex == "Male", age >= 18) |>
  select(height) |>
  drop_na() |>
  ggplot(aes(x = height)) +
    geom_histogram(bins = 50) +
    labs(
      title = "Male Adult Height in the US in 2010",
      x = "Height (cm)",
      y = "Count",
      caption = "Source: National Health and Nutrition Examination Servey")
```

```{r}
#| cache: TRUE
#| echo: FALSE

fit_male_height <- brm(
  formula = height ~ 1,
  data = nhanes,
  family = gaussian,
  silent = 2,
  refresh = 0,
  seed = 12)
```

```{r}
#| echo: FALSE

tbl_regression(fit_male_height, intercept = TRUE)
```

```{r}
#| label: plot
#| echo: FALSE
ndata <- tibble(.rows = 1)

fit_male_height |>
  add_predicted_draws(newdata = ndata) |>
  ggplot(aes(x = .prediction)) +
  geom_histogram(aes(y = after_stat(count/sum(count))), bins = 100) +
  labs(
    title = "Posterior for Height of Random Male",
    subtitle = "Uncertainty for a single individual is much greater than for the expected value",
    x = "Height (cm)",
    y = "Probability",
    caption = "Data source: NHANES") +
  scale_x_continuous(labels = scales::number_format()) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))
```

```{r}
#| echo: FALSE

fit_male_height |>
  add_predicted_draws(newdata = ndata) |>
  mutate(tall = if_else(.prediction > 180, TRUE, FALSE)) |>
  summarize(odds = mean(tall))
```

